---
title: "Text mining with tidy data principles: topic modeling"
author: "Julia Silge"
output: html_document
---

## Download data

First download data to use for our embeddings:

```{r}
library(tidyverse)

cheeses <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-06-04/cheeses.csv') |>
  filter(!is.na(flavor))

glimpse(cheeses)
```

So many cheeses!

```{r}
sample(cheeses$flavor, 10)
```

Cheese data from <https://www.cheese.com/> via [Tidy Tuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2024/2024-06-04/readme.md)


What do you predict will happen if we run the following code?

**PREDICT WITH YOUR NEIGHBOR BEFORE YOU RUN**

```{r}
library(tidytext)

dtm <- cheeses |>
    mutate(id = row_number()) |> 
    unnest_tokens(word, flavor) |> 
    anti_join(get_stopwords(), by = "word") |>  
    count(id, word) |>  
    bind_tf_idf(word, id, n) |> 
    cast_dfm(id, word, tf_idf)

dtm
```


## Let's create cheese embeddings 🧀

```{r}
library(wordsalad)

flavor_embeddings <- 
    cheeses |>
    mutate(flavor = str_remove_all(flavor, ",")) |>
    pull(flavor) |>
    ___

flavor_embeddings
```

Let's create an overall average embedding for each cheese (using `mean()`):

```{r}
tidy_cheeses <-
    cheeses |>
    mutate(cheese_id = row_number()) |>
    ___(word, flavor) |>
    left_join(flavor_embeddings, by = c("word" = "tokens")) |>
    ___(cheese_id, cheese, milk, country, type) |>
    summarize(across(V1:V10, ~ mean(.x, na.rm = TRUE)), .groups = "drop")

tidy_cheeses
```

## Cheese similarity 🧀

```{r}
embeddings_mat <- 
    tidy_cheeses |> 
    select(V1:V10)  |> 
    as.matrix()

row.names(embeddings_mat) <- cheeses$cheese
embeddings_similarity <- embeddings_mat / sqrt(rowSums(embeddings_mat * embeddings_mat))
embeddings_similarity <- embeddings_similarity %*% t(embeddings_similarity)
dim(embeddings_similarity)
```

What are the highest probability words in each topic?

**U N S C R A M B L E**

```{r}
filter(cheese == "Manchego") |> 
  
select(cheese, country, flavor)

cheeses |> 
```

What are the _most_ similar cheeses to Manchego?

```{r}
enframe(embeddings_similarity["Manchego",], name = "cheese", value = "similarity") |>
  arrange(-similarity)
```

```{r}
cheeses |> 
  filter(cheese %in% c("Beemster Classic", "Butternut", "Loma Alta")) |> 
  select(cheese, country, flavor)
```


```{r}
cheeses |> 
  filter(cheese %in% c(___)) |> 
  select(cheese, country, flavor)
```


What about the _least_ similar cheeses to Manchego?

```{r}
enframe(embeddings_similarity["Manchego",], name = "cheese", value = "similarity") |>
  arrange(___)
```

## Cheesy similarity 🧀

```{r}
cheeses |> 
  ___(cheese %in% c("Bossa", "St Cera", "Minger")) |> 
  select(cheese, country, flavor)
```
